Enhancing instance-level constrained clustering through differential evolution

### 2019-02-11 Papers/SHADE/paperSHADE.tex
Nuevos resultados y secciones en paper SHADE

\usepackage{lineno,hyperref}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{adjustbox}
\usepackage{chngpage}
\usepackage{setspace}
\usepackage{amsfonts}
\usepackage[ruled, lined, onelanguage, linesnumbered]{algorithm2e}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newcommand{\myfloatalign}{\centering}
\modulolinenumbers[5]

@@

In order to carry out this task we will make use the widely known frequentist non parametric two-tailed Wilcoxon test, as well as the lesser-known Bayesian sign test.

\subsection{Applying Wilcoxon test to our results}

\textcolor{red}{Buscar a alguien que sepa explicarme que cojones es lo que hace el Keel. Las hipótesis no pueden ser las que he planteado y problemente el alpha no se use para calcular el estadístico T}

We will apply the Wilcoxon test for each of the measures obtained as a result, namely: ARI, Unsat and Time. Remember that the Wilcoxon test is a hypothesis test, whose hypotheses are established as:

@@

	\item $H_0$: differences between pairs of results follow a symmetric distribution around zero.

	\item $H_1$: differences between pairs of results do not follow a symmetric distribution around zero.

@@

It is also necessary to establish a confidence level to obtain the statistical values that will allow us to make a decision about $H_0$. In this case we consider a confidence level of 95\%, which means that the value of $\alpha$ for the calculation of the statistic $T$ will be $\alpha = 1 - 0.95 = 0.05$. Table \ref{tab:freqTest} shows the statistical values obtained using Wilcoxon test for each comparison.

\begin{table}[!htp]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	\begin{tabular}{cccc}
		\hline
		VS & $R^{+}$ & $R^{-}$ & P-value \\ \hline 
		ARI & 3203.5 & 1746.5 & 0.006936\\
		Time & 4008.0 & 1042.0 & 0\\  
		Unsat & 3829.5 & 1120.5 & 0.000002\\ \hline 
	\end{tabular}
	\caption{Results obtained by the Wilcoxon test for algorithm SHADE (vs BRKGA)}
	\label{tab:freqTest}
\end{table}

It is worth noting that, in the case of ARI, this is a maximization problem, while in the remaining two measures we try to minimize.

The results are clear, in all cases $p-value < \alpha$, which means that we can reject the null hypothesis. We conclude that there are significant differences between the two methods in favour of SHADE+LS.

@@

>>>>

\usepackage{graphics, float, url}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{lineno,hyperref}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{adjustbox}
\usepackage{chngpage}
\usepackage{setspace}
\usepackage{amsfonts}
\usepackage{subcaption}
\usepackage{float}
\usepackage[ruled, lined, onelanguage, linesnumbered]{algorithm2e}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\newcommand{\myfloatalign}{\centering}
\modulolinenumbers[5]

\usepackage{epstopdf}
\epstopdfDeclareGraphicsRule{.tiff}{png}{.png}{convert #1 \OutputFile}
\AppendGraphicsExtensions{.tiff}

@@

In order to carry out this task we will make use the widely known frequentist non-parametric Wilcoxon's test, as well as the lesser-known Bayesian sign test.

\subsection{Applying Wilcoxon's test to our results}

We will apply the Wilcoxon's test for each of the measures obtained, namely: ARI, Unsat and Time. Remember that the Wilcoxon's test is a hypothesis test, whose hypotheses are established as:

@@

	\item $H_0$: differences between pairs of results follow a symmetric distribution around $\mu$.

	\item $H_1$: differences between pairs of results do not follow a symmetric distribution around $\mu$.

@@

In this case we set $\mu = 0$, and work with a confidence level of 95\%, which means that the significance level is 0.05 ($\alpha = 0.05$). Table \ref{tab:freqTest} shows the statistical values obtained using Wilcoxon's test for each comparison.

\begin{table}[!htp]
	\centering
	\setlength{\tabcolsep}{7pt}
	\renewcommand{\arraystretch}{1.4}
	\begin{tabular}{cccccc}
		\hline
		\multirow{2}{*}{Measure} & \multirow{2}{*}{$R^{+}$} & \multirow{2}{*}{$R^{-}$} & \multirow{2}{*}{P-value}
		&  \multicolumn{2}{c}{Median} \\
		\cline{5-6}
		& & & & BRKGA + LS & SHADE + LS \\
		\hline
		ARI & 3088 & 1665 & 0.01051 & 0.30356 & 0.32573\\
		Time & 4008 & 1042 & 0.000000344 & 1204.967 & 1202.947 \\  
		Unsat & 3082.5 & 745.5 & 0.000000767 & 5.851 & 3.072 \\ 
		\hline 
	\end{tabular}
	\caption{Results obtained by the Wilcoxon's test for algorithm SHADE (vs BRKGA)}
	\label{tab:freqTest}
\end{table}

For all three considered measures, $\alpha < P-value$, therefore in all cases we can reject $H_0$ and find that there are significant differences between the two methods. To choose the method that gets the lead we observe the medians, we choose the one with greater or lesser median depending on whether it is a matter of maximization or minimization. In conclusion, we can safely admit that Wilcoxon's test provides empirical evidence in favour of SHADE + LS.

\subsection{Applying Bayesian sign test to our results}

Te Bayesian sign test is the Bayesian version of the frequentist non-parametric tests. It allows us to conclude whether there are significant differences between two sets of results.\cite{carrasco2017rnpbst}

It is based on deriving the distribution of a parameter $\rho$ according to the difference between the sets of results. We will refer to the set of results obtained by BRKGA - LS as $A$, and to the set of results obtained with SHADE + LS as $B$. It is also necessary to define the region of practical equivalence (rope) $[r_{min}, r_{max}]$, for those cases in which the difference between $A$ and $B$ is not significant.

To get the distribution of $\rho$ we count the number of times the advantage is for $A$, the number of times where there are no significant differences, and the number of times the advantage is for $B$. We then calculate the weights of a Dirichlet distribution and sample it. The result of this sampling will be a set of triplets in the form of $[(\rho < r_{min}), (\rho \in rope), (\rho > r_{max}]$.

\textcolor{red}{Traducir el párrafo de abajo al inglés}

Podemos obtener una representación del conjunto de tripletas en forma de un diagrama de calor. Para ello, hacemos corresponder los vértices de un triángulo equilátero con los tres valores de una tripleta. Para representar un valor, trazamos una linea paralela al lado opuesto del vértice asociado al valor que queremos representar, a una distancia relativa de el calculada en base al valor cuestión. El punto en el que intersecan las líneas asociadas a los tres valores es el punto asociado a la tripleta que los contiene. Cabe destacar que, dado que los valores de cada tripleta representan una distribución de probabilidad, su suma siempre vale 1, y por tanto siempre existe un punto de intersección entre las líneas que los representan.

\begin{figure}[ht!]
	\centering
	\begin{subfigure}{.45\textwidth}
		\includegraphics[width=1\linewidth]{Figures/BayesSignoARI.pdf}
		\caption{ARI}
	\end{subfigure}
	\begin{subfigure}{.45\textwidth}
		\includegraphics[width=1\linewidth]{Figures/BayesSignoTime.pdf}
		\caption{Time}
	\end{subfigure}
	\begin{subfigure}{.45\textwidth}
		\includegraphics[width=1\linewidth]{Figures/BayesSignoUnsat.pdf}
		\caption{Usat}
	\end{subfigure}
	\caption{Heat diagrams for each measure}
\end{figure}

@@

\begin{figure}[bth]
	\myfloatalign
	%\subfloat[ARI]
	{\includegraphics[width=.45\linewidth]{Figures/BayesSignoARI.pdf}} \quad
	%\subfloat[Time]
	{\includegraphics[width=.45\linewidth]{Figures/BayesSignoTime.pdf}} \quad
	%\subfloat[Unsat]
	{\includegraphics[width=.45\linewidth]{Figures/BayesSignoUnsat.pdf}} \quad
	\caption{Heat diagrams for each measure obtained.}
	\label{img:heatDiag}
\end{figure}
